---
title: "World Cup 2026 — Fixtures Refresh"
output: html_document
---

This document is deployed to POSIT Connect as a **scheduled R Markdown**. Each
scheduled render runs the gated `run_refresh()` pipeline in `refresh_job.R`,
which decides per tick whether to do real work.

**Schedule on Connect:** `* * * * *` (every minute). The job is self-gating:

- **Idle ticks** (no match live, no match about to kick off) exit silently in
  ~1 pin read — no external API calls, no leaderboard rebuild, no log entry.
- **Live-window ticks** (any match in `[kickoff − 2 min, kickoff + 110 min]`
  for group / `+ 180 min` for knockout, OR any match with status
  `IN_PLAY` / `PAUSED`) do the full pipeline:
  - Pull ESPN's public scoreboard (every tick, no auth, no published limit)
    for live scores, ET, and PK shootout counts
  - Pull football-data.org **once per 10 min** (throttled via a tiny pin
    `wc26_last_football_data_at`) for the canonical schedule + slower
    'truth' fallback
  - Write the merged result to `wc26_fixtures`
  - Rebuild the `wc26_leaderboard` snapshot so the app reads it in one op
  - Append one row to `wc26_refresh_log` (rolling, last 100 runs)

See `r/refresh.R` for the gate (`should_run_refresh`, `is_live_window`) and
the throttle, and `r/api_espn.R` for the ESPN ET/PK extraction logic.

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r run-refresh}
# Run from the same directory as this .Rmd so source() paths resolve.
source("refresh_job.R")
```

Rendered at `r format(Sys.time(), "%Y-%m-%d %H:%M:%S %Z", tz = "UTC")`.
